---
title: "Checkbox functions"
author:
- Josh DeClercq
- Department of Biostatistics
- Vanderbilt University Medical Center
date: "<small>`r Sys.Date()`</small>"
output:
  rmdformats::robobook:
    thumbnails: no
    lightbox: true
    gallery: no
    highlight: tango
    use_bookdown: yes
    toc_depth: 2
    fig_caption: yes
    code_folding: hide
    embed_fonts: no
    keep_md: false
    number_sections: true

---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)

require(Hmisc)
require(rms)
require(ggplot2)
require(lubridate)
require(reshape2)
require(magrittr)
require(dplyr)
require(knitr)
require(kableExtra)
require(tidyr)
require(stringr)
require(forcats)
require(labelVector)
require(DT)
library(captioner)
require(gtsummary)
require(gt)
require(reactable)
require(purrr)


devtools::source_url("https://raw.githubusercontent.com/jjdeclercq/Jmisc/main/Jmisc.R")
source("checkbox_funs.R")

select <- dplyr::select
``` 

# Generate data
```{r}
set.seed(100)
trib.x <- tibble::tribble(
   ~nv,     ~check,
   "1",    "Mouse",
   "2",      "Rat",
   "3",      "Cat",
   "4",      "Dog",
   "5",   "Donkey",
   "6",   "Monkey",
   "7",   "Turtle",
   "8", "Hedgehog",
   "9", "Blue jay",
  "10",    "Rhino",
  "11",    "Other",
  "12",     "None")


# check_data(10) %>% jgtt()
# 
# check_data_repeat(10, 5)

X <- data.frame(id = 1:100, rep = sample(1:6, 100, replace = TRUE))

c1 <- map(X$id, .f = check_data) %>% bind_rows()%>%
  left_join(., trib.x, by = "nv") %>%
  mutate(checkbox = paste(checkbox, nv, sep = "_"), check = ifelse(x==1, check, NA)) %>%
  select(-x, -nv) %>%
  pivot_wider(., names_from = "checkbox", values_from = "check", values_fill = NA) 


cb <- map2(.x = X$id, .y = X$rep, .f = check_data_repeat) %>% bind_rows()%>%
  left_join(., trib.x, by = "nv") %>%
  mutate(checkbox = paste(checkbox, nv, sep = "_"), check = ifelse(x==1, check, NA)) %>%
  select(-x, -nv) %>%
  pivot_wider(., names_from = "checkbox", values_from = "check", values_fill = NA) 


# j.label4(cb, collect.labels(df))
cb <- set_label( cb ,
 id = 'ID',
 rri = 'Repeat instance',
 site = 'Site',
 checkbox_1 = 'Mouse',
 checkbox_2 = 'Rat',
 checkbox_3 = 'Cat',
 checkbox_4 = 'Dog',
 checkbox_5 = 'Donkey',
 checkbox_6 = 'Monkey',
 checkbox_7 = 'Turtle',
 checkbox_8 = 'Hedgehog',
 checkbox_9 = 'Blue jay',
 checkbox_10 = 'Rhino',
 checkbox_11 = 'Other',
 checkbox_12 = 'None')

cb %<>% clear.label.class()

c1 <- set_label( c1 ,
 id = 'ID',
 site = 'Site',
 checkbox_1 =  'What animals did you see? (choice=Mouse)',
 checkbox_2 =  'What animals did you see? (choice=Rat)',
 checkbox_3 =  'What animals did you see? (choice=Cat)',
 checkbox_4 =  'What animals did you see? (choice=Dog)',
 checkbox_5 =  'What animals did you see? (choice=Donkey)',
 checkbox_6 =  'What animals did you see? (choice=Monkey)',
 checkbox_7 =  'What animals did you see? (choice=Turtle)',
 checkbox_8 =  'What animals did you see? (choice=Hedgehog)',
 checkbox_9 =  'What animals did you see? (choice=Blue jay)',
 checkbox_10 = 'What animals did you see? (choice=Rhino)',
 checkbox_11 = 'What animals did you see? (choice=Other)',
 checkbox_12 = 'What animals did you see? (choice=None)')

c1 %<>% clear.label.class()
```

## simple checkbox data
```{r}
c1 %>% clear.labels() %>% head(10) %>% jgtt(., col.names = FALSE)
```

## repeating checkbox
```{r}
cb %>% clear.labels() %>% head(10) %>% jgtt(., col.names = FALSE)
```



# checkbox_gather

## Simple checkbox data

### Data frame output

Returns data frame that can be joined to original data. Columns may be more suited to other summary tables or modeling.

```{r}
checkbox_gather(c1, selection = "checkbox", id.var = c("id")) %>% head()%>% jgtt()
```

### Change data type

With non-repeating data, 'any' and 'total' are equivalent. However, setting `count = "total"` returns numeric columns. 

```{r}
checkbox_gather(c1, selection = "checkbox", id.var = c("id"), count = "total")%>%head() %>% jgtt()
```

### Summary output

Checkboxes are non-mutually exclusive, so percentages will not sum to 100%.

**Interpretation:** 20 people included checkbox_1 among their selections.

```{r}
checkbox_gather(c1, selection = "checkbox", id.var = c("id"), output = "summary")
```

### Account for no selections made

Even if there is a checkbox specifically for "none" or "none of the above", there is still room for data entry errors. Setting `add.zero = TRUE` will append a new row to the data, and anyone with no other selections will be counted here.

**Interpretation:** 4 people had zero boxes selected.

```{r}
checkbox_gather(c1, selection = "checkbox", id.var = c("id"), output = "summary", 
                add.zero = TRUE)
```

### Add variable labels

Setting `toggle.names = TRUE` will use the variable labels rather than the variable names.

```{r}
checkbox_gather(c1, selection = "checkbox", id.var = c("id"), output = "summary", 
                add.zero = TRUE, toggle.names = TRUE)
```

### Remove trailing description

Changing `simple.names = TRUE` will clean up the trailing descriptor. Note, this feature does not work if `count = "both"`.

```{r}
checkbox_gather(c1, selection = "checkbox", id.var = c("id"), output = "summary", 
                add.zero = TRUE, toggle.names = TRUE, simple.names = TRUE)
```

### Clean up labels

Often redcap variable labels for checkboxes contain a lot of extraneous information. Adjusting `tidy.labels = TRUE` should fix this assuming the pattern is of "Long description (choice=**DATA ITEM**)"

```{r}
checkbox_gather(c1, selection = "checkbox", id.var = c("id"), output = "summary", 
                add.zero = TRUE, toggle.names = TRUE, simple.names = TRUE,
                tidy.labels = TRUE)

```

### Report checkbox stats

An alternative to individual checkbox summaries is aggregated summaries. For non-repeating data, setting `stats` to `only` will present the number of zero selections as well as the total number of selections each participant made.

**Interpretation:** 11 participants made 4 selections, while 22 participants only reported one each.

```{r}
checkbox_gather(c1, selection = "checkbox", id.var = c("id"),  
                stats = "only", toggle.names = TRUE, output = "summary")
```

### Add in stratafication variable

Summaries can be stratified by putting the desired variable at `by.var = "site"`.

**Interpretation:** 7 people at site A and 4 people at site B reported seeing 4 animals.

```{r}
checkbox_gather(c1, selection = "checkbox", id.var = c("id"),  by.var = "site",
                stats = "only", toggle.names = TRUE, output = "summary")
```

## Repeating data - record level

To produce summaries on the record (ID) level using repeating data, simply leave `repeat.var = NULL`

### Count any

**Interpretation:** 33 people reported seeing a mouse at least once at site A.

```{r}
checkbox_gather(cb, selection = "checkbox", id.var = c("id"), 
                by.var = "site", simple.names = FALSE,
                count = "any", stats = "none", toggle.names = TRUE, add.zero = TRUE, output = "summary") 
```

### Count total

**Interpretation:** At site A, 17 people reported seeing 1 mouse, 14 saw 2 mice and 2 people saw 3 mice. (17 + 14 + 2 = 33, which matches the `count = "any"` output above.)

```{r}
checkbox_gather(cb, selection = "checkbox", id.var = c("id"), 
                by.var = "site", simple.names = FALSE,
                count = "total", stats = "none", toggle.names = TRUE, add.zero = TRUE, output = "summary") 
```

### Count both

With repeating measurements reported on the record level, the "any" and "total" counts give different results. Note: Here `simple.names = TRUE` will not change the output of the variable labels, as the additional information is crucial to differentiating the two summaries.

```{r}
checkbox_gather(cb, selection = "checkbox_2", id.var = c("id"), 
                by.var = "site", simple.names = FALSE,
                count = "both", stats = "none", toggle.names = TRUE,  output = "summary") 
```

### Stats 

Reporting on this level also yields a few additional aggregate summaries: the number of unique selections made and the number of times the form was repeated within each record.

**Interpretation:** 5 people filled out information for 2 repeating forms. The median (IQR) number of animals reported was 8 (4 - 13) at site A, while the median number of unique animals seen was 7 (4 - 9). The difference here is if someone reporting seeing a monkey on each of 5 different excursions, but no other animals, their number of selections made would be 5, but their number of unique selections would be 1.



```{r}
checkbox_gather(cb, selection = "checkbox", id.var = c("id"), 
                by.var = "site", 
                 stats = "only", toggle.names = TRUE, output = "summary")
```

### Add spanner

Adding `spanner.size = 2, spanner.text = "Site"` adds information about the stratification variable. `spanner.size` must match the number of levels in `by.var`. (Note: these two arguments are passed to `jgt` which itself is a generalization of `tbl_summary`.)

```{r}
checkbox_gather(cb, selection = "checkbox_2", id.var = c("id"), 
                by.var = "site", simple.names = FALSE,
                count = "both", stats = "none", toggle.names = TRUE,  output = "summary",
                spanner.size = 2, spanner.text = "Site") 
```

### Rowwise percentages

Adding `percent = "row"` will make report percentages calculated across each row rather than column-wise.

**Interpretation:** Of the 52 people who reported seeing a Rat, 44% of them were from Site B.

```{r}
checkbox_gather(cb, selection = "checkbox_2", id.var = c("id"), 
                by.var = "site", simple.names = FALSE,
                count = "both", stats = "none", toggle.names = TRUE,  output = "summary",
                spanner.size = 2, spanner.text = "Site", percent = "row") 
```

## Repeating data - observation level
### Stats 

Here we see that the repeating data has 361 observations.

**Interpretation:** 10 observation-level records had zero selections made. This does not necessarily mean that 10 people did not fill out a form one time. It could be possible that one person had 10 observations in the data, and did not make a selection in any of them. 

```{r}
checkbox_gather(cb, selection = "checkbox", id.var = c("id"), 
                by.var = "site", repeat.var = "rri",
                 stats = "only", toggle.names = TRUE, output = "summary")
```

### Count both

In the observation level summaries, the results for "total" and "any" are the same.

```{r}
checkbox_gather(cb, selection = "checkbox_2", id.var = c("id"), 
                by.var = "site", simple.names = FALSE,repeat.var = "rri",
                count = "both", stats = "none", toggle.names = TRUE,  output = "summary") 
```

# checkbox_tally

Rather than the participant or the observation being the unit of study, this function aggregates the checkbox data and uses that as the identifier of interest. 

Many of the same arguments are used in `checkbox_tally`.

## non-repeating data

Data are transformed so that there are as many observations as there were boxes selected. The argument `col.name` controls what the aggregated variable is named in the summary table.

**Interpretation:** A rhino was observed 24 times across both sites, accounting for 9.7% of all boxes selected. However, the `none` and `zero` counts are included in the denominator, which may not produce the desired outcome. See the subsequent table for the alternative calculation.

```{r}
checkbox_tally(c1, "checkbox", id.var = "id", by.var = "site", add.zero = TRUE, 
               col.name = "Animal", spanner.size = 2, spanner.text = "Site" )
```

## removing levels

In this case, both the none and other levels were removed by removing from them from data prior to piping into the function (`c1 %>% select(-checkbox_11, -checkbox_12) `)

**Interpretation:** Of the 218 animals of interest, 10.1% of observations made were a dog.

```{r}
c1 %>% select(-checkbox_11, -checkbox_12) %>% 
checkbox_tally(., "checkbox", id.var = "id", by.var = "site", add.zero = FALSE, 
               col.name = "Animal", spanner.size = 2, spanner.text = "Site" )
```

## repeating data - by site

Repeating data is handled similarly to the simple case, because the unit of study here are the checkbox values, not the observation or record. 

```{r}
checkbox_tally(cb, "checkbox", id.var = "id", by.var = "site", add.zero = FALSE, 
               col.name = "Animal", spanner.size = 2, spanner.text = "Site" )
```

## repeating data - by repeat variable

Change the `by.var` to the repeating variable, to get a summary of the distribution of animals observed at each time point.

```{r}
checkbox_tally(cb, "checkbox", id.var = "id", by.var = "rri", add.zero = FALSE, 
               col.name = "Animal", spanner.size = 6, spanner.text = "Observation" )
```


# checkbox_intersect

Constructs an UpSet plot to visualize which selections were most commonly made together. Inputs are similar to `checkbox_gather`.

## Simple data

Note: the number of columns was reduced to lessen the number of intersections for the sake of interpretation.

**Interpretation:** 14 people only saw a cat. 4 people reported seeing both a Mouse and a Rat. While 1 person saw a Mouse, a Rat and a Cat.


```{r}
checkbox_intersect(c1 %>% select(1:6), "checkbox", id.var = "id", add.zero = TRUE, tidy.labels = TRUE)
```

## Repeating data - observation level
```{r}
checkbox_intersect(cb %>% select(1:7), "checkbox", id.var = "id", add.zero = FALSE, repeat.var = "rri")
```

## Repeating data - record level

Excluding `repeat.var` with repeating data will greatly increase the number of intersections.

```{r}
checkbox_intersect(cb %>% select(1:7), "checkbox", id.var = "id", add.zero = TRUE)
```


```{r eval = FALSE}

checkbox.by2(cb, "checkbox", id.vars = c("id"), by.var = "site", count = "all", byvar.reorder = c(1,3,2,4), add.zero = FALSE)

lookup_names(cb, selection = "checkbox")

# 
# stats: only all none

cb %>% select(1, NULL) %>% left_join(., lp, by = c("id", "rri"))

cb %>% select(1, site, contains("checkbox")) %>%
  pivot_longer(., c(-id, -site), values_drop_na = TRUE) %>% 
  select(value, site) %>% jgt(., order.cat = TRUE, by = "site", overall = TRUE)



checkbox_tally(cb, "checkbox", id.var = "id", by.var = "site", add.zero = TRUE, 
               col.name = "Animal", spanner.size = 2, spanner.text = "Site" )

checkbox.upset2(cb, "checkbox", id.vars = c("id"))







checkbox_intersect(c1, "checkbox", id.var = "id", add.zero = TRUE)
checkbox_intersect(cb, "checkbox", id.var = "id", add.zero = TRUE, repeat.var = "rri")

tidy_labels(hd.cv, "tx_2")

lookup_names(hd.cv, "tx_2")


lookup_names(hd.cv, "tx_2", tidy.labels = TRUE)

data.frame(var = names(),
           input = formals(checkbox_gather) %>% paste()) %>%
  mutate(o = paste0(var, " = ", input, ", ")) %$% o

# ffun <- function(fun){
#   A <- deparse(substitute(fun))
#   b <- formals(fun)
#   C <- data.frame(var = names(b),
#            input = b %>% paste()) %>%
#   mutate(o = paste0(var, " = ", input, ", ")) %$% o
#   
#   cat(A, "(",C, ")")
# }
# 
# ffun(checkbox_gather)
# 
# checkbox_gather( dat = ,  selection = ,  id.var = NULL,  by.var = NULL,  count = any,  tidy.labels = FALSE,  repeat.var = NULL,  stats = n,  toggle.names = TRUE,  simple.names = FALSE,  add.zero = FALSE,  output = df,  ... = ,  )

fun.fun <- function(fun){
a <- gsub("function ", deparse(substitute(fun)), paste(head(capture.output(args(fun)), -1), collapse = "\n" ))
cat(a)
}

fun.fun(jgt)
args(jgt)
# checkbox_gather(c1, selection = "checkbox", id.var = c("id"),  
#                 stats = "only", toggle.names = FALSE, output = "summary")
# checkbox_gather(cb, selection = "checkbox", id.var = c("id"), 
#                 by.var = "site", 
#                  stats = "only", toggle.names = TRUE, output = "summary")
# checkbox_gather(cb, selection = "checkbox", id.var = c("id"), 
#                 by.var = "site", repeat.var = "rri",
#                  stats = "only", toggle.names = TRUE, output = "summary")
```




```{r}
# cb_labels <- collect.labels(cb) %>% filter(grepl("checkbox", variable)) %>%
#   mutate(any = paste(label, "(any)"),
#          total = paste(label, "(total)"),
#          any_var = paste0("any_", variable),
#          total_var = paste0("total_", variable))
# 
# lookup.any <- cb_labels$any_var 
# names(lookup.any) <- cb_labels$any
# lookup.total <-   cb_labels$total_var 
# names(lookup.total) <- cb_labels$total



# cb %>% group_by(id, site) %>% 
#   summarise(across(contains("checkbox"), ~sum(!is.na(.x)), .names = "total_{.col}"), 
#                                         n.obs =n()) %>% 
#   rowwise() %>% mutate(across(contains("checkbox"), ~yesno(.x>0), .names = 'any{stringr::str_remove(.col, "total")}'),
#     n.selected = sum(across(contains("total"))),
#                        n.unique = sum(across(contains("total"))>0)) %>% ungroup() %>%
#   rename(any_of(c(lookup.any, lookup.total))) %>%
#   select(contains("total"), -id, site) %>%
#   jgt(., by = "site", overall = TRUE, one_row_binary = TRUE)
```


```{r eval = FALSE}
A <- matrix(data = c(a = c(0, 1,1,1), 
                b = c(-1,0,1,1),
                c = c(-1, -1, 0,1),
                d = c(-1, -1, -1, 0)), 
       nrow = 4, byrow = TRUE) 

A <- matrix(data = c(a = c(0, 1,1,1), 
                b = c(0,0,1,1),
                c = c(0, 0, 0,1),
                d = c(0, 0, 0, 0)), 
       nrow = 4, byrow = TRUE) 

B <- matrix(data = c(a = c(0, 1,-1,1), 
                b = c(-1,0,1,1),
                c = c(1, -1, 0,1),
                d = c(-1, -1, -1, 0)), 
       nrow = 4, byrow = TRUE) 

B <- matrix(data = c(a = c(0, 1,1,1), 
                b = c(0,0,1,1),
                c = c(0, 0, 0,1),
                d = c(0, 0, 0, 0)), 
       nrow = 4, byrow = TRUE) 

rownames(A) <- colnames(A) <- c("a", "b", "c", "d")
# rownames(B) <- colnames(B) <- c("a", "b", "c", "d")

rownames(B) <-colnames(B) <- c("b", "e", "d", "f")


Vx <- expand.grid(unique(c(colnames(A), colnames(B))), unique(c(colnames(A), colnames(B)) ), stringsAsFactors = FALSE) %>%
  rename(item = Var1, name = Var2)


as.data.frame(A) %>% rownames_to_column() %>% pivot_longer(-1) %>%
  group_by(rowname) %>% summarise(v = sum(value))


comp1 <- left_join(Vx, 
          bind_rows(as.data.frame(A) %>% rownames_to_column("item") %>% pivot_longer(-1),
          as.data.frame(B) %>% rownames_to_column("item") %>% pivot_longer(-1)),
          by = c("item", "name")) %>% distinct() 

comp2 <- comp1 %>% 
  arrange(item) %>% filter(value ==1) %>% select(name = item, comp = name)

comp3 <- full_join(comp1, comp2, by = "name") %>% distinct() %>% arrange(item)%>% filter(value == 1, !is.na(comp)) %>%
  select(item, name = comp, value)

bind_rows(comp1, comp3) %>%distinct() %>% arrange(item) %>%
  group_by(item, name) %>% summarise(value = sum(value, na.rm = TRUE)) %>% 
  pivot_wider(., names_from = "name", values_from = "value", values_fill = NA)
```


```{r eval = FALSE}
A %*% t(A) %*% matrix(data = c(1, 1,1,1),nrow = 4, byrow = TRUE)

B <- matrix(data = c(a = c(0, 1,1,1, 0, 0), 
                b = c(0,0,1,1, 1, 1),
                c = c(0, 0, 0,1, 0, 0),
                d = c(0, 0, 0, 0, 0, 1),
                e = c(0, 0, 0, 1, 0, 1),
                f = c(0, 0, 0, 0, 0, 0)), 
       nrow = 6, byrow = TRUE) 

C <- matrix(data = c(a = c(1, 1,1,1, 0, 0), 
                b = c(1,1,1,1, 1, 1),
                c = c(1, 1, 1,1, 0, 0),
                d = c(1,1,1,1, 1, 1),
                e = c(0, 1, 0, 1, 1, 1),
                f = c(0, 1, 0, 1, 1, 1)), 
       nrow = 6, byrow = TRUE) 

colnames(B) <- c("a", "b", "c", "d", "e", "f")
rownames(B) <- c("a", "b", "c", "d", "e", "f")

B %*% t(B) %*% matrix(data = c(1, 1,1,1, 1, 1),ncol = 1, byrow = TRUE)
B %*% t(B) %*% matrix(data = c(1, .5,1,.5, 1, 1),ncol = 1, byrow = TRUE)

B %*% t(B) %*%(diag(c(4,1,4, 1, 4,4), 6 )*0.5) %*% matrix(data = c(1, 1,1,1, 1, 1),ncol = 1, byrow = TRUE)
```


```{r eval = FALSE}
`%>>%` <- function(a, b){
  if(!is.data.frame(a)){
  RE <- data.frame(item = a, item2 = b)
  }else{ 
   nr <- nrow(a) + 1
    RE <- bind_rows(a, data.frame(item = c(a$item, a$item2[nrow(a)]), item2 = rep(b, nr))) %>% distinct()
  }
  
  return(RE)
} 
"A" %>>% "B" %>>% "C"
g <- "A" %>>% "B" %>>% "I" %>>% "E"
h <- "B" %>>% "C" 
hh <- "C" %>>% "D"
h2 <- "D" %>>% "E"
h3 <- "E" %>>% "F"
h4 <- "F" %>>% "G"
h5 <- "G" %>>% "H"
H <- bind_rows(g, h, hh, h2, h3, h4, h5)

k <- bind_rows(H %>% mutate(value =1),
data.frame(item = H$item2, item2 = H$item) %>% mutate(value = -1)) %>% 
  distinct() 

left_join(k, k %>% rename(item2 = item, comp = item2), by = c("item2", "value") ) %>% distinct() %>% 
  filter(item != comp|is.na(comp)) %>%
  pivot_longer(., -c("item", "value"), names_to = "x", values_to = "item2", values_drop_na = TRUE) %>%
  select(-x)%>% distinct() %>%
  mutate(item = fct_reorder(item, value, sum)) %>%
  mutate(item2 = factor(item2, levels = levels(item))) %>%
  arrange(desc(item), desc(item2) ) %>%
  pivot_wider(., names_from = "item2", values_from = "value") %>% 
  select(item, all_of(rev(levels(.$item))))
```

```{r eval = FALSE}
k <- bind_rows(H %>% mutate(value =1),
data.frame(item = H$item2, item2 = H$item) %>% mutate(value = -1)) %>% 
  distinct() %>% mutate(n =1)

i <- 0 
j<- 100
round <- 0
while(i < j){
  i <- nrow(k)
    round <- round+1
  
  k2 <- left_join(k %>% select(-n), 
                  k %>% select(-n) %>% rename(item2 = item, comp = item2), 
                  by = c("item2", "value") ) %>% 
    distinct() %>% 
  filter(item != comp|is.na(comp)) %>%
  pivot_longer(., -c("item", "value"), names_to = "x", values_to = "item2", values_drop_na = TRUE) %>%
  select(-x)%>% distinct() 
  
  k <- full_join(k, k2, c("item", "item2", "value")) %>% mutate(n = replace_na(n, round))
  
  j <- nrow(k)

}
  
k %>% select(-n) %>% 
  mutate(item = fct_reorder(item, value, sum)) %>%
  mutate(item2 = factor(item2, levels = levels(item))) %>%
  arrange(desc(item), desc(item2) ) %>%
  pivot_wider(., names_from = "item2", values_from = "value") %>% 
  select(item, all_of(rev(levels(.$item))))
```


```{r eval = FALSE}
k <- bind_rows(j %>% mutate(value =1),
data.frame(item = j$name, name = j$item) %>% mutate(value = -1)) %>% 
  group_by(item, name) %>% summarise(value = sum(value)) 

left_join(k, k %>% rename(name = item, comp = name), by = c("name", "value") ) %>% distinct() %>% 
  filter(item != comp|is.na(comp)) %>%
  pivot_longer(., -c("item", "value"), names_to = "x", values_to = "item2", values_drop_na = TRUE) %>%
  select(-x)%>% 
  group_by(item, item2) %>% summarise(value = sum(value)) %>%
  mutate(item = fct_reorder(item, value, sum)) %>%
  mutate(item2 = factor(item2, levels = levels(item))) %>%
  arrange((item), desc(item2) ) %>%
  pivot_wider(., names_from = "item2", values_from = "value") %>% 
  select(item, all_of(levels(.$item)))
```

